Weather Data Integration and Assimilation System\\

### 2020-02-16 results/sec_3-observations.tex
Fix: All test plan

After running the All test plan with 60 minutes (24 data points), it observed the data summary of \cref{tab:obs_all_60_min_summary}. It performed 311k of sample requests.

@@

\cref{subse:obs_test_plan_all_30min} discussed the All test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII grid files per each insert request. It performed round up to 311k of sample requests which are almost similar to \cref{subse:obs_test_plan_all_60min} processed samples.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_response_times_vs_threads.png}
    \caption{Load testing with 30 minutes data - Response Time vs Threads}
    \label{fi:test_obs_all_30m_response_vs_threads}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_res_latencies_against_hits.png}
    \caption{Load testing with 30 minutes data - Latency against server hits}
    \label{fi:test_obs_all_30m_latency}
\end{figure}
\cref{fi:test_obs_all_30m_latency} graph provides a better overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second. This graph also concludes that over time latency does not change very much. But during the peak load, it shows some variation in the insert and retrieves of Grid timeseries.
When compared to \cref{fi:test_obs_all_60m_latency}, the latency for insert and retrieve Grid timeseries increase by some amount.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_response_times_vs_threads.png}
    \caption{Load testing with 15 minutes data - Response Time vs Active Threads}
    \label{fi:test_obs_all_15m_response_vs_threads}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_res_latencies_against_hits.png}
    \caption{Load testing with 15 minutes data - Latency against server hits}
    \label{fi:test_obs_all_15m_latency}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_transaction_throughtput_vs_threads.png}
    \caption{Load testing with 15 minutes data - Transaction Throughput vs Threads}
    \label{fi:test_obs_all_15m_throughtput}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_response_times_percentiles.png}
    \caption{Load testing with 15 minutes data - Response times Percentiles}
    \label{fi:test_obs_all_15m_latency_percentile}
\end{figure}
\cref{fi:test_obs_all_15m_latency_percentile} visually shows the summary of \cref{tab:obs_all_15_min_summary} latency up to 90\% percentile. With higher request size data, the \acrshort{wdias} able to process the requests without significant change in latency up to 90\% percentile.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
    \caption{Load testing with 15 minutes data with enabled auto-scaling - Latency against server hits}
    \label{fi:test_obs_all_auto_15m_latency}
\end{figure}
\cref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15min data while auto-scaling enabled for \acrshort{k8s}.
This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan.
When compared to \cref{fi:test_obs_all_15m_latency}, throughout the test period, the latency spikes become less.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
    \caption{Load testing with 15 minutes data with enabled auto-scaling - Transaction Throughput vs Threads}
    \label{fi:test_obs_all_auto_15m_throughtput}
\end{figure}

>>>>

After running the test plan with 60 minutes (24 data points), it observed the data summary of \cref{tab:obs_all_60_min_summary}. It performed 311k of sample requests.

@@

\cref{subse:obs_test_plan_all_30min} discussed the test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII grid files per each insert request. It performed round up to 311k of sample requests which are almost similar to \cref{subse:obs_test_plan_all_60min} processed samples.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_response_times_vs_threads.png}
    \caption{Load testing with 30 minutes of data - Response Time vs Threads}
    \label{fi:test_obs_all_30m_response_vs_threads}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_30m_res_latencies_against_hits.png}
    \caption{Load testing with 30 minutes of data - Latency against server hits}
    \label{fi:test_obs_all_30m_latency}
\end{figure}
\cref{fi:test_obs_all_30m_latency} graph provides a better overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second. This graph also concludes that over time latency does not change very much. But during the peak load, it shows some variation in the insert and retrieves of Grid timeseries.
When compared to \cref{fi:test_obs_all_60m_latency}, the latency for insert and retrieve Grid timeseries increase by some amount.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_response_times_vs_threads.png}
    \caption{Load testing with 15 minutes of data - Response Time vs Active Threads}
    \label{fi:test_obs_all_15m_response_vs_threads}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_res_latencies_against_hits.png}
    \caption{Load testing with 15 minutes of data - Latency against server hits}
    \label{fi:test_obs_all_15m_latency}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_transaction_throughtput_vs_threads.png}
    \caption{Load testing with 15 minutes of data - Transaction Throughput vs Threads}
    \label{fi:test_obs_all_15m_throughtput}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all/obs_all_15m_response_times_percentiles.png}
    \caption{Load testing with 15 minutes of data - Response times Percentiles}
    \label{fi:test_obs_all_15m_latency_percentile}
\end{figure}
\cref{fi:test_obs_all_15m_latency_percentile} visually shows the summary of \cref{tab:obs_all_15_min_summary} latency up to 90\% percentile. With higher request size data, the \acrshort{wdias} able to process the requests without significant change in latency up to 90\% percentile.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
    \caption{Load testing with 15 minutes of data with enabled auto-scaling - Latency against server hits}
    \label{fi:test_obs_all_auto_15m_latency}
\end{figure}
\cref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15min data while auto-scaling enabled for \acrshort{k8s}.
This graph show that over the time \acrshort{wdias} were able to keep the latency constant over the test plan.
When compared to \cref{fi:test_obs_all_15m_latency}, throughout the test period, the latency spikes become less.

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_transaction_throughtput_vs_threads.png}
    \caption{Load testing with 15 minutes of data with enabled auto-scaling - Transaction Throughput vs Threads}
    \label{fi:test_obs_all_auto_15m_throughtput}
\end{figure}
